VSEARCH clustering

### 2020-10-27 exploratory/2020/sub4_vsearch.Rmd
Update vsearch plots with gg db; newer optifit version

For now, just going to show silva v4 for reference-clustering with the soil dataset.
Will expand to include more variables later.
```{r silva-soil-only}
dat_filt <- dat %>% filter(ref %in% c('silva', NA), 
                           region %in% c('bact_v4', NA),
                           dataset == 'soil') %>% 
  select(dataset, ref, region, tool, method, mcc, sec, mem_gb, numotus, fraction_mapped) %>% 
  mutate(tool_method = glue("{tool}_{method}"))

dat_filt %>% pivot_longer(c(mcc, sec, mem_gb), names_to = 'metric') %>% 
  ggplot(aes(x = method, y = value, color = tool)) +
  geom_boxplot() +
  facet_wrap('metric', scales = 'free')
```

@@

```{r mcc}
dat_filt %>% ggplot(aes(x = tool, y = mcc, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors) +
  ylim(0, 1)
```

@@

```{r runtime}
dat_filt %>% ggplot(aes(x = tool, y = sec, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors)
dat_filt %>% ggplot(aes(x = tool, y = mem_gb, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors)
```

@@

```{r fraction}
dat_filt %>% filter(method == 'closed') %>% 
  ggplot(aes(x = tool, y = fraction_mapped, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  ylim(0, 1)
```

>>>>

Preliminary results with just the soil dataset vs greengenes below.
Will expand to include more datasets later.
```{r vsearch-soil-only}
dat_filt <- dat %>% filter(ref %in% c('gg', NA), 
                           region %in% c('bact_v4', NA),
                           dataset == 'soil') %>% 
  select(dataset, ref, region, tool, method, mcc, sec, mem_gb, numotus, fraction_mapped) %>% 
  mutate(tool_method = glue("{tool}_{method}"))

dat_filt %>% pivot_longer(c(mcc, sec, mem_gb), names_to = 'metric') %>% 
  ggplot(aes(x = method, y = value, color = tool)) +
  geom_boxplot() +
  facet_wrap('metric', scales = 'free') + 
  labs(caption = "For reference clustering, the soil dataset was fit to the greengenes db.") +
  theme(axis.title = element_blank())
```

@@

```{r vsearch_mcc}
dat_filt %>% ggplot(aes(x = tool, y = mcc, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors) +
  ylim(0, 1)
```

@@

```{r vsearch_runtime}
dat_filt %>% ggplot(aes(x = tool, y = sec, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors)
dat_filt %>% ggplot(aes(x = tool, y = mem_gb, color = dataset)) +
  geom_boxplot() +
  facet_wrap('method') +
  scale_color_manual(values = dataset_colors)
```

@@

```{r vsearch_fraction}
dat_filt %>% filter(method == 'closed') %>% 
  ggplot(aes(x = tool, y = fraction_mapped, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  ylim(0, 1)
```
